---
title: "Learning Tidy Models"
author: "Tim Essam"
format: html
editor: visual
---

## Tidy Models

Tidy models is a framework for running machine learning models. It consists of an ecosystem of modeling packages. This primer will cover the basics of the framework and some basic DS concepts.

## Getting Started

Load the tidymodels un

```{r}
library(tidymodels)
```

Testing and Training Data

Training data is always set aside at the beginning as this is used to validate the model.

use the `set.seed(42)` function to ensure that you get reproducible results. (If your seed setting drives your model performance, you likely have bigger issues w/ your model).

Testing data can be divided up in numerous ways. Resampling the testing data is one way to divy up the testing data. You can also use cross-validation (randomly assign data to different folds), where you withhold some of the data. Say two-thirds of the data are used to train the data and one-third is used to test the data. Tidy models has a `vfold_cv()` function you can use to cross-validate your model.

Say you have 100 data points, you can sample 10, run your model, then use the 2nd sample of n

Bootstrapping - different way of making resamples. Take your original training set and draw with replacement until you get to N samples. Whatever is not picked goes into the assessment set. You can use the `bootstraps()` function to do this.

Each method has different types of bias/variance trade-offs.

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
